Glyph-maps for Visually Exploring Temporal Patterns in Climate Data and Models

### 2012-03-05 revision/paper.tex
fixed a ref, and .

  \caption{(Top) Glyph-map of predicted temperature anomaly data (GISTEMP),
    from 1950-2010. Increasing trends can be seen over most of the
    USA, with varying degrees of increase. Some isolated locations
    exhibit steep declines, and inclines, perhaps indicative of some
    isolated data problems. Note that, the reference lines are
    straight, but they look curved because of the Z\"ollner optical
    illusion. (Bottom) Legend showing ranges of individual glyphs}
  \label{fig:gistemp-pred}
\end{figure}

@@

Glyph-maps work best when displayed in the coordinate system in which the grid is rectangular and regular.  For example, the GISTEMP grid is 2$^o$ square and is displayed treating longitude and latitude as cartesian coordinates in Figure \ref{fig:gistemp-pred}.  For regularly gridded data, this results in icons that are rectangles of equal size.  It is often preferable to display maps as a projection of the geographical coordinates which preserves a property of interest, area for example. When a projection is desired a choice needs to be made between applying the projection to the completed glyph-map, or to just the spatial locations.  When the completed glyph-map is projected the icons are no longer rectangles of the same size but they do retain their space filling property.  When applying a projection to the spatial locations and then constructing a glyph-map, the grid becomes irregular.

>>>>

  \caption{(Top) Glyph-map of predicted temperature anomaly data
    (GISTEMP), on reduced range temperature 1950-2010. Increasing
    trends can be seen over most of the USA, with varying degrees of
    increase. Some isolated locations exhibit steep declines, and
    inclines, perhaps indicative of some isolated data problems. Note
    that, the reference lines are straight, but they look curved
    because of the Z\"ollner optical illusion. (Bottom) Legend showing
    temperature and temporal ranges of individual glyphs.}
  \label{fig:gistemp-pred}
\end{figure}

@@

Glyph-maps work best when displayed in the coordinate system in which the grid is rectangular and regular.  For example, the GISTEMP grid is 2$^o$ square and is displayed treating longitude and latitude as Cartesian coordinates in Figure \ref{fig:gistemp-pred}.  For regularly gridded data, this results in icons that are rectangles of equal size.  It is often preferable to display maps as a projection of the geographical coordinates which preserves a property of interest, area for example. When a projection is desired a choice needs to be made between applying the projection to the completed glyph-map, or to just the spatial locations.  When the completed glyph-map is projected the icons are no longer rectangles of the same size but they do retain their space filling property.  When applying a projection to the spatial locations and then constructing a glyph-map, the grid becomes irregular.
